From a centralized certification systems to a more internet-like one

### 2015-12-24 paper.tex
DANE -> Done
Miss one point on DANE is the last kilometer faillure.

% Define document title and author
	\title{Trustability of certification systems}
	\author{Alexandre Kervadec
	\thanks{Tutor : A.Guermouche}}
	\markboth{University of Bordeaux -- Master 2 Computing Sciences - Networking and mobile systems}{}
	\maketitle

@@

DANE is not implemented yet, but a IETF team is working on the standard.\\
It has begin with a simple assert: why use a new trust infrastructure if we already have to use DNS to resolve a domain name?\\
From here, DNS must be securised, knowing that it is easily to set a MITM with DNS cache poisoning \cite{bor08} \cite{aa04}. That is the main purpose of DNSSEC: secure DNS. DANE allow to store keys in DNS. Thereby, \verb$www.example.org$ would be able to secure \verb$https://www.example.org$ without using a suspicious third part, just by putting its keys in the domain name that it controls. By its arborescent nature, \verb$example.org$ shall not be able to cheat on \verb$example.com$.

@@

>>>>

% Define document title and author
	\title{From a centralized certification systems to a more internet-like one}
	\author{Alexandre Kervadec
	\thanks{Tutor : A.Guermouche}}
	\markboth{University of Bordeaux -- Master 2 Computing Sciences - Networking and mobile systems}{}
	\maketitle

@@

DANE is not implemented yet, but a IETF team is working on the standard.\\
It has begin with a simple assert: why use a new trust infrastructure if we already have to use DNS to resolve a domain name?\\
From here, DNS must be securised, knowing that it is easily to set a MITM with DNS cache poisoning \cite{aa04} using the Kaminsky attack \cite{bor08}. That is the main purpose of DNSSEC: secure DNS. DANE allow to store keys in DNS. Thereby, \verb$www.example.org$ would be able to secure \verb$https://www.example.org$ without using a suspicious third part, just by putting its keys in the domain name that it controls. By its arborescent nature, \verb$example.org$ shall not be able to cheat on \verb$example.com$.\\

Lets give us an example:\\
From the classic schem, we have \textit{Alice}, the subscriber (\verb$alice.example.com$), \textit{Bob} its client, and \textit{Charlie}, the serious AC. There are three different scenarios:
\begin{itemize}
	\item \textit{Type 0:} Alice has got a certificate delivered by Charlie and is really satisfied by it. But Alice is afraid that \textit{Oscar} (a bad AC) forge a false certificate for its website. So Alice uses DANE to tell in DNS that Charlie and only Charlie is its AC.
	\item \textit{Type 1:} Alice has got a certificate delivered by Charlie, but fear that Charlie give its certificate to bad people. So Alice uses DANE to publish in DNS the origin of its certificate.
	\item \textit{Type 2:} that is the \textit{max scenario} in DANE. Alice doesn't trust ACs anymore, so it decides to emite it via DANE on DNS, that gives the entire responsability on DNS servers. 
\end{itemize}

This type is in a new register called TLSA\footnote{TLSA doesn't stand for anything: it is just the name of the RRtype (Record Resource type).} in DNS. Her is an example of a TLSA register:\\
\begin{Verbatim}[fontsize=\small]
_443._tcp.www.example.com. IN TLSA (
	0 0 1 d2abde240d7cd3ee6b4b28c54df0&34b9
	7983a1d16e8a410e4561cb106618e971 )
\end{Verbatim}
With:
\begin{itemize}
	\item \verb$443$ : the port used.
	\item \verb$tcp$ : the protocole used.
	\item \verb$www.example.com$ the domain name.
	\item \verb$0 x x$ : the type used, here it is a type 0 (\verb$1 x x$ for type 1 and \verb$2 x x$ for type 2).
	\item The rest is the certificate itself.
\end{itemize}

As we said before, DNS is not secured, so DNSEC has been deployed. DNSSEC is a protocol that allow to the DNS server (master) ti encrypt and sign its answer with a public key cryptographic system. It also permit to return a \verb$NXDOMAIN$ type (''No Such Domain'').\\
Nervertheless DNSSEC has some vulnaribilities such as:
\begin{itemize}
	\item Replay attacks
	\item Attacks against intermediaries: because of the hierarchic and centralized approch of DNS (there is only one root), the responsability of intermediaries is really high and a remote control by a thief should be bad (the thief controls the domain thus). History has proved that some of those intermediaries are not that trustworthy \cite{dan08} \cite{utk11}.
\end{itemize}

To make a conclusion about DANE, we have multiple points to point out:
\begin{itemize}
	\item Introducing a new register TLSA shall be very complicated, knowing that things are not moving that fast in DNS\footnote{Like it use to be with EDNS introduction few years ago.}.
	\item The validation necessity end to end is quite disturbing knowing that there is no standart and deployable solution for wide use  about the last kilometer securisation.
	\item DNSSEC is not possible behind a DNS proxy (which filter/break DNS answers to the point of creating a DoS for all TLS services.
\end{itemize}

Therefor, DANE is on a good way, particulary for communications between servers, where there is no (not much) constraints of security are (more) easily achievable.

@@

\bibitem{dan08} Dancho Danchev. Hackers hijack dns records of high profile new zealand sites. http://m.zdnet.com/blog/security/hackers-hijack-dns-records-of-high-profile-new-zealand-sites/3185, 2008.

\bibitem{utk11} Utkarsh. Domaining.com hacked. http://dotsutra.com/domain-names/industry-news/domaining-com-hacked/, 2011.
